The Small World Network Effect in Open Source Project Teams \author{Kevin Peterson\\ \small \texttt{pete1968@umn.edu} }

### 2013-11-16 paper/main.tex
A little more analysis.

\textit{Clustering Coefficient (Transitivity}\\
We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
\[C^\delta = 3 \times \frac{\text{number of triangles}}
                    {\text{number of connected triples}}\]

\textit{Clustering Coefficient (Average}\\
Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.

@@

$Q$ and $C^\Delta$ both indicate a non-normal distribution, as shown by the large standard deviation. This observation indicates a propensity towards the extremes of these measurements. This is further reinforced by the distribution of $Q$ shown in figure \ref{fig:q_distribution}. This figure indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of either 0 or 1.\\

@@

>>>>

\textit{Clustering Coefficient (Transitivity)}\\
We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
\[C^\delta = 3 \times \frac{\text{number of triangles}}
                    {\text{number of connected triples}}\]

\textit{Clustering Coefficient (Average)}\\
Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.

@@

$Q$ and $C^\Delta$ both indicate a non-normal distribution, as shown by the large standard deviation. This observation indicates a propensity towards the extremes of these measurements. This is further reinforced by the distribution of $Q$ shown in figure \ref{fig:q_distribution}. This figure indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of close to either 0 or 1.\\

@@

To validate the hypothesis, we expect to find that medium values of $C^\Delta$ will be correlated with more popular projects. To explore this possibility, we first compare the popularity given $C^\Delta$ values as shown in figure \ref{fig:cc_popular}. The $C^\Delta$ values do display the U-shaped characteristic as compared to popularity, which aligns with the findings of Uzzi \textit{et. al}\cite{uzzi2005collaboration}. It is important to note, however that, the standard deviation is high, as shown in both \ref{fig:summary_stats} and the significant difference between the mean and median results.
